---
title: "Analyzing Responses to the 2018 Stack Overflow Developer Survey"
output: html_notebook
---
I have created this data analysis notebook to help me learn about R, xgboost, the data.table package, and the tidyverse packages. The **dataset** that I will be exploring is the responses to the 2018 Stack Overflow Developer Survey, which can be found [here][data]. Other resources/references can be found at the [end](#references) of this notebook. 

Note: the survey dataset is _not_ included in this GitHub repository.

## Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(data.table)
```

## Data
```{r}
dt <- fread("data/survey_results_public.csv")
```

### Visualization

## Model
TODO: use xgboost to predict a variable

## References
Dataset:

* [2018 Stack Overflow Developer Survey][data]

General R:

* Wickham and Grolemund's open source book: [R for Data Science](http://r4ds.had.co.nz/index.html)

data.table:

* https://www.listendata.com/2016/10/r-data-table.html
* https://github.com/Rdatatable/data.table/wiki/Getting-started
* https://s3.amazonaws.com/assets.datacamp.com/blog_assets/datatable_Cheat_Sheet_R.pdf
* https://www.r-bloggers.com/understanding-data-table-rolling-joins/

Inspiration to guide my data visualization:

* The kaggle notebook ["Novice to Grandmaster - What Data Scientists say?"](https://www.kaggle.com/ash316/novice-to-grandmaster/notebook)


[data]: https://insights.stackoverflow.com/survey